Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Update comment
Fix typo
Add an other comment

BDD includes TDD, amongst other software development methodologies,
but with a terminology and mindset shifted towards
specification instead of testing.
In BDD, specifications can be used for
automatic testing.  BDD-style TDD has been pioneered by
RSpec~\cite{rspec}.  In this paper, we explore how to apply the TDD
aspect of BDD to Haskell.

@@

    \begin{itemize}
        \item test discovery is not an aspect of BDD, only an emphasis
            on automating things is an aspect of BDD, so that
            \emph{testing is more fun} and \emph{things e.g. work with
            CI}.  This are two things, but both justify automation.
            We only need this to justify our discussion of Cabal
            integration and automatic test discovery.  If we remove
            those, we do not state that ``automation is an important
            aspect of BDD''.  This may be a solution.
        \item @mkl your previous version stated, that BDD includes
            other things (ATDD!), but that we do not cover them.  This
            is very important.  And I think that meaning got lost with
            the change, hence the revert.
    \end{itemize}
\end{quote}

@@

\subsection{Automatic discover of specs}

>>>>

BDD includes TDD, amongst other software development methodologies,
but with a terminology and mindset shifted towards
specification instead of testing.
In BDD, specifications can be used for
automatic testing.

\begin{quote}
    sol: maybe like so?  In addition to \emph{automating things}, this
    would also motivate \ref{sec:code-doc}, which is IMHO not
    motivated very well.

    BDD is meant to be an enjoyable experience for the developer.  It
    provides compared to TDD it provides a much nicer syntax that
    makes tests very easy to read.  And like TDD it puts emphasis on
    test automation, to take load from the shoulders of developers.
\end{quote}

BDD-style TDD has been pioneered by
RSpec~\cite{rspec}.  In this paper, we explore how to apply the TDD
aspect of BDD to Haskell.

@@

    \begin{itemize}
        \item test discovery is not an aspect of BDD, only an emphasis
            on automating things is an aspect of BDD, so that
            \emph{testing is more fun} and \emph{things e.g. work with
            CI}.  This are two different things, but both justify automation.
            We only need this to justify our discussion of Cabal
            integration and automatic test discovery.  If we remove
            those, we do not need to state that ``automation is an important
            aspect of BDD''.  This may be a solution.
        \item @mkl your previous version stated, that BDD includes
            other things (ATDD!), but that we do not cover them.  This
            is very important.  And I think that meaning got lost with
            the change, hence the revert.
    \end{itemize}
\end{quote}

@@

\subsection{Automatic discovery of specs}
